The \dealii{} Library, Version 8.5

### 2017-03-19 8.5/paper.tex
older pgfplots version
Sorry, my version is much older and I am too lazy to update.
spell checking, language fixes, etc.

\pgfplotsset{compat=1.12}

@@

\item We realized that static code analyzers are valuable tools to improve
  and maintain the quality of the code in our library on top off build and
  regression tests for a variety of setups using
  \href{https://cdash.kyomu.43-1.org/index.php?project=deal.II}{CDash}.
  This release was tested with
  \href{http://cppcheck.sourceforge.net/}{Cppcheck},
  \href{https://www.viva64.com/en/pvs-studio/}{PVS-Studio} and
  \href{https://scan.coverity.com/}{Coverity-Scan}. For the latter the
  current status can be observed
  \href{https://scan.coverity.com/projects/deal-ii}{online}.

@@

The \texttt{CellDataStorage} class is an integrated mechanism to safely
store user-defined data, such as that required at each computation point,
within each cell. Although the same was previously achieved through the use
of a cell \texttt{user\_pointer}, it required users to manage this data
themselves. This data is now treated as a first-class citizen to \dealii{}.

@@

Quadrature points computed using this mapping lie on the exact
geometrical objects, and tangent and normal vectors computed using
this class are tangent and normal to the underlying geometry. This is
in constrast with the \texttt{MappingQ} and \texttt{MappingQGeneric}
classes, which approximate the geometry using a polynomial of some
order, and then compute the normals and tangents using the
approximated surface.

Currently only first order transformations are implemented, and an
assertion is thrown if the user requests any higher order
transformations, for example, the hessian of the mapping.

@@

An additional feature of the \texttt{LinearOperator} suite is the defintion
of a \texttt{schur\_complement} operator and its associated condensation
and post-processing \texttt{PackagedOperation}s. An operator representing
the Schur complement of a block system can be declared and, through the
delayed evaluation offered by \texttt{PackagedOperation}s, reused on any
number of vector systems.

@@

The \verb!FE_Enriched! finite element implements a partition of unity
finite element method (PUM) by Babuska and Melenk which enriches a standard
finite element with an enrichment function multiplied with another (usually
linear) finite element. This allows to include in the finite element space
a priori knowledge about the partial differential equation being solved
which in turn improves the local approximation properties of the spaces.
The user can also use enriched and non-enriched finite elements in
different parts of the domain.
\verb|DoFTools::make_hanging_node_constraints()| function can automatically
make the resulting space $C^0$ continuous. Existing \verb|SolutionTransfer|
class can be used to transfer the solution during $h$\,-adaptive refinement
from a coarse to a fine mesh under the condition that all child elements
are also enriched.

@@

The 8.5.0 release includes around 20
\href{https://www.dealii.org/8.5.0/doxygen/deal.II/changes_between_8_4_and_8_5.html}{
incompatible changes}; see \cite{changes85}. The majority of these changes
should not be visible to typical user codes; some remove previously
deprecated classes and functions, and the majority change internal
interfaces that are not typically used in user codes. However, a number of
incompatible changes a worth mentioning.
\begin{itemize}
  \item High-order Lagrange elements, both continuous \verb!FE_Q! and
    discontinuous \verb!FE_DGQ! types, now use the nodal points of the
    Gauss--Lobatto quadrature formula as support points, rather than the
    previous equidistant ones. For cubic polynomials and higher, the point
    distribution has thus changed and, consequently, the entries in
    solution vectors will look different as compared to the previous
    version. Note, however, that using the Gauss--Lobatto points as nodal
    points results in a much more stable interpolation, including better
    iteration counts in most iterative solvers.
  \item
    The library does not instantiate template versions with \texttt{long
    double} any more. If you need template versions with \texttt{long
    double} make sure to include the corresponding \texttt{templates.h}
    header file.
  \item
    The \texttt{ParameterGUI} has been moved to a separate repository.
\end{itemize}

@@

There are various ways to reference \dealii{}. To acknowledge the use of a
particular version of the library, reference the present document. For up
to date information and bibtex snippets for this document see:
\begin{center}
 \url{https://www.dealii.org/publications.html}
\end{center}

>>>>

\pgfplotsset{compat=1.9}

@@

\item Static code analyzers are valuable tools to improve
  and maintain the quality of the code in our library in addition to build and
  regression tests for a variety of setups using
  \href{https://cdash.kyomu.43-1.org/index.php?project=deal.II}{CDash}.
  This release was tested with
  \href{http://cppcheck.sourceforge.net/}{Cppcheck},
  \href{https://www.viva64.com/en/pvs-studio/}{PVS-Studio} and
  \href{https://scan.coverity.com/}{Coverity-Scan}. For the latter the
  current status can be observed
  \href{https://scan.coverity.com/projects/deal-ii}{online}.

@@

The \texttt{CellDataStorage} class is an integrated mechanism to safely
store user-defined data within each cell, such as a coefficient at each quadrature point.
Although the same was previously achieved through the use
of a cell \texttt{user\_pointer}, it required users to manage this data
themselves. This data is now treated as a first-class citizen to \dealii{}.

@@

Quadrature points computed using this mapping lie on the exact
geometrical objects, and tangent and normal vectors computed using
this class are tangent and normal to the underlying geometry. This is
in contrast with the \texttt{MappingQ} and \texttt{MappingQGeneric}
classes, which approximate the geometry using a polynomial of some
order, and then compute the normals and tangents using the
approximated surface.

Currently only first order transformations are implemented, and an
assertion is thrown if the user requests any higher order
transformations, for example, the Hessian of the mapping.

@@

An additional feature of the \texttt{LinearOperator} suite is the definition
of a \texttt{schur\_complement} operator and its associated condensation
and post-processing \texttt{PackagedOperation}s. An operator representing
the Schur complement of a block system can be declared and, through the
delayed evaluation offered by \texttt{PackagedOperation}s, reused on any
number of vector systems.

@@

The \verb!FE_Enriched! finite element implements a partition of unity
finite element method (PUM) by Babuska and Melenk which enriches a standard
finite element with an enrichment function multiplied with another (usually
linear) finite element. This allows including 
a priori knowledge about the partial differential equation being solved
in the finite element space,
which in turn improves the local approximation properties of the spaces.
The user can also use enriched and non-enriched finite elements in
different parts of the domain.
\verb|DoFTools::make_hanging_node_constraints()| function can automatically
make the resulting space $C^0$ continuous. The existing \verb|SolutionTransfer|
class can be used to transfer the solution during $h$\,-adaptive refinement
from a coarse to a fine mesh under the condition that all child elements
are also enriched.

@@

The 8.5 release includes around 20
\href{https://www.dealii.org/developer/doxygen/deal.II/changes_between_8_4_and_8_5.html}{
incompatible changes}; see \cite{changes85}. The majority of these changes
should not be visible to typical user codes; some remove previously
deprecated classes and functions, and the majority change internal
interfaces that are not typically used in user codes. However, a number of
incompatible changes are worth mentioning.
\begin{itemize}
  \item High-order Lagrange elements, both continuous \verb!FE_Q! and
    discontinuous \verb!FE_DGQ! types, now use the nodal points of the
    Gauss--Lobatto quadrature formula as support points, rather than the
    previous equidistant ones. For cubic polynomials and higher, the point
    distribution has thus changed and, consequently, the entries in
    solution vectors will look different as compared to the previous
    version. Note, however, that using the Gauss--Lobatto points as nodal
    points results in a much more stable interpolation, including better
    iteration counts in most iterative solvers.
  \item
    The library does not instantiate template versions with \texttt{long
    double} any more. If you need template versions with \texttt{long
    double} make sure to include the corresponding \texttt{templates.h}
    header file.
  \item
    The \texttt{ParameterGUI} has been moved to a separate repository.
\end{itemize}

@@

There are various ways to reference \dealii{}. To acknowledge the use of the
current version of the library, \textbf{please reference the present document}. For up
to date information and bibtex snippets for this document see:
\begin{center}
 \url{https://www.dealii.org/publications.html}
\end{center}
